My title

### 2024-03-19 paper/paper.qmd
Update 46-63 in quarto to simplify the table making code. Code still does not work when trying to render. Might just remove

library(tidyverse)
library(here)

@@

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

>>>>

library(tidyverse)
library(here)
library(readr)

```{r}
##chooseCRANmirror(graphics = FALSE)  # Select a CRAN mirror
##install.packages("devtools")        # Install the devtools package
```

```{r}
##install.packages("devtools")
##install.packages("kableExtra")
##devtools::install_github("haozhu233/kableExtra")
```

```{r}

library(knitr)
library(kableExtra)

# Define the list
dflist <- list(variables = c("All Americans", "Race", "Gender", "Political Affiliation", "Level of Education"),
               observations = c("All the following groups", "Self-identified race of participants", "Male/Female", "Democrat/Republican/Other", "College Degree or Higher/Highschool Diploma/No Highschool Diploma")
)

# Convert the list to a data frame
df <- as.data.frame(dflist)

# Display the data frame as a table with kableExtra
kbl(df) %>%
  kable_classic(full_width = FALSE, html_font = "Cambria")

@@

(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
